Template for indicator documentation

### 2023-10-17 DRAFT_Connectivity.Rmd
rm duplicate java code in final code block

<!-- Fill in which ecosystem the indicator belongs to, as well as the ecosystem characteristic it should be linked to. It's OK to use some Norwegian here -->
```{r, echo=F}
Ecosystem <- "Våtmark"
Egenskap  <- "Konnektivitet"
ECT       <- "Landscape and seascape characteristics"
Contact   <- "Vegar Bakkestuen"
```

@@

@@

### SEEA EA (UN standard) {#seea-con}
In the framework of the United Nations System of Environmental-Economic Accounting (SEEA EA), the "Connectivity" indicator can be classified as a C1 "Landscape and seascape characteristics" indicator.

@@

# Skift til scenariet "Konnektivitet uten infrastruktur" ved å fjerne infrastrukturdataene
infrastruktur = ee.Image(0); // Nullstiller infrastruktur til et tomt bilde
var omraderMedGjennomsnittligAvstandUtenInfrastruktur = omraderGeometries.map(calculateMeanDistance);

@@

The sclaed "Connectivity" values is created by dividing the result without infrastructure by the result that includes infrastructure. This ratio will give you a value between 0 and 1, where 0 represents complete disruption of connectivity due to infrastructure, and 1 represents undisturbed natural connectivity.

>>>>

<!-- Fill in which ecosystem the indicator belongs to, as well as the ecosystem characteristic it should be linked to. It's OK to use some Norwegian here -->
```{r, echo=F}
Ecosystem <- "Våtmark"
Egenskap  <- "Landskapsøkologiske mønstre"
ECT       <- "Landscape and seascape characteristics"
Contact   <- "Vegar Bakkestuen"
```

@@

It is also possible to create a time series for this indicator, but this is not yet done. See [GitHub issue](https://github.com/NINAnor/ecosystemCondition/issues/145).

@@

### SEEA EA (UN standard) {#seea-con}
In the framework of the United Nations System of Environmental-Economic Accounting (SEEA EA), the _Connectivity_ indicator can be classified as a **C1 Landscape and seascape characteristics** indicator.

@@

@@

The scaled "Connectivity" values are created by dividing the result without infrastructure by the result that includes infrastructure. This ratio will give you a value between 0 and 1, where 0 represents complete disruption of connectivity due to infrastructure, and 1 represents undisturbed natural connectivity.
